Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-07-18 main.tex
updated references and bugfix for plots

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

@@

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

@@

\begin{abstract}
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

@@

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. \textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

@@

We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc). At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation. \citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse. \textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.

\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas. These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution. At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr. We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$. These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions. This threshold decreases the required run-time by factors of a few. The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}

@@

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local \textbf{thermal} Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.

The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
\begin{equation}
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample from
the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$. \textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution. \textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

@@

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback. We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. \textbf{This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle. The edges of this spherical region will only partially overlap grid cells. We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.} We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).

@@

Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor. Integrating this gives the total probability at any given time as
\begin{equation}
P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
\end{equation}
where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$. This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
\textbf{In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle. For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova. We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.}

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. {\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations. \textbf{Our chemical work only includes contributions from H, He, and H$_2$ to n$_e$.} Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

@@

\textbf{H2 changes:} The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component. The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run. The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation. During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1. Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated. However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

>>>>

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\pdfoutput=1 
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

@@

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}

@@

\begin{abstract}
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

@@

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles. Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

@@

We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc). At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation. \citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse. A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.

Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas. These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution. At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr. We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$. These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions. This threshold decreases the required run-time by factors of a few. The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)

@@

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.

The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
\begin{equation}
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample from
the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$. The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation. We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution. By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

@@

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback. We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle. The edges of this spherical region will only partially overlap grid cells. We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately. We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).

@@

Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor. Integrating this gives the total probability at any given time as
\begin{equation}
P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
\end{equation}
where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$. This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle. For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova. We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations. Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$. Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component. The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run. The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation. During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1. Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated. However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
